A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-04 4_method.tex
move method images
fix language mistakes (reviewer 1.7)

\paragraph{Beading propagation}
The beading information is then broadcast throughout the ST from central regions outward,
so that each unmarked node $v$ knows the beading of the marked node on top of the ramp on which $v$ is placed.
We first broadcast the beading information upward from all marked nodes,
so that we can then deal with beading conflicts in a downward phase.
This the downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.

>>>>

\paragraph{Beading propagation}
The beading information is then broadcast throughout the ST from central regions outward,
so that each unmarked node $v$ knows the beading of the marked node on top of the ramp on which $v$ is placed.
We first broadcast the beading information upward from all marked nodes,
so that we can then deal with beading conflicts in a downward phase.
\revise{This the}{The} downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
